Formatting Instructions for ICLR 2025 \\ Conference Submissions

### 2024-09-12 ICLR25/formula.tex
update

This is the formula to compute improvement of nodes two layers before.

@@

\begin{definition}
	Continue the assumption in Definition \ref{3layer}. We define function $D$ layer by layer.

@@

	\begin{align*}
		&w_0 = \sum_C D(c)W_{cd}\\
		&w_1 = \min(\UB(d),v(d)+w_0)\\		
		&D(d) =
		\begin{cases}
			w_1-v({d}), & \text{if }W_{da} > 0 \text{ and } \LB(d)\geq 0\\
		k(d)(w_1-v({d})), & \text{if }W_{da} > 0 \text{ and } \LB(d)< 0\\
		\ReLU(w_1)-v(\hat{d})	, & \text{if }  W_{da} < 0
		\end{cases}\\
		&D(a) = -\sum_c D(d)W_{da}
	\end{align*}
\end{definition}

>>>>

$D(a)$ is the estimation of improvement of upper bound of $a$ by openning node $b$. This is the formula to compute improvement of nodes two layers before.

@@

\begin{definition}
	Continue the assumption in Definition \ref{3layer}. To compute the improvement of of upper bound of $a$ by $b$, we define function $D$ layer by layer.

@@

	\begin{align*}
		&w_0 = \sum_C D(c)W_{cd}\\
		&w_1 = \min(\UB(d),v(d)+w_0)\\		
		&D(d) =
		\begin{cases}
			w_1-v({d}), & \text{if }W_{da} > 0 \text{ and } \LB(d)\geq 0\\
		k(d)(w_1-v({d})), & \text{if }W_{da} > 0 \text{ and } \LB(d)< 0\\
		\ReLU(w_1)-v(\hat{d})	, & \text{if }  W_{da} < 0
		\end{cases}\\
		&D(a) = -\sum_c D(d)W_{da}
	\end{align*}
\end{definition}$D(a)$ is the estimation of improvement of upper bound of $a$ by opening node $b$.
